---
title: "TidyTuesdayRiddlerDecember"
author: "Andrew Couch"
date: "12/7/2020"
output: html_document
---

Video: https://www.youtube.com/watch?v=otWUI8Aam0g&list=PLJfshcspBCYeJeO8YFT5e5HxuYOb5a_1W&index=13&t=645s

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

From Christopher “CJ” Halverson comes a bibliophilic game of Secret Santa:

Every year, CJ’s family of five (including CJ) does a book exchange for Christmas. First, each person puts their name in a hat. The hat is shaken, and then each person draws a random name from the hat and gifts that person a book. However, if anyone draws their own name, they all put their names back into the hat and start over.

What is the probability that no one will draw their own name?

```{r}
# Try to replicate the process using sampling without replacement
first_run <- sample(5, size = 5, replace = FALSE) 
first_run

# Check if people drew their own names
first_run == c(1, 2, 3, 4, 5)

# Count how many people drew their own name
sum(as.numeric(first_run == c(1, 2, 3, 4, 5)))

# Check if no one drew their own name
sum(as.numeric(first_run == c(1, 2, 3, 4, 5)))==0
```


```{r}
# Create function to use as a simulation
book_exchange <- function(){
  sum(as.numeric(sample(5, size = 5, replace = FALSE) == c(1, 2, 3, 4, 5)))==0
}

```
```{r}
sim <- replicate(100000, book_exchange()) %>% 
  as.numeric() %>% 
  mean()

1-sim
```

```{r}
crossing(trials = 1:1000000,
         draws = 1:5) %>% 
  group_by(trials) %>% 
  mutate(res = sample(5, size = 5, replace = FALSE)) %>% 
  ungroup() %>% 
  mutate(drew_own_name = draws == res) %>% 
  count(trials, drew_own_name) %>% 
  pivot_wider(names_from = drew_own_name, values_from = n, values_fill = 0) %>% 
  count(`FALSE` == 5) %>% 
  mutate(n = n / sum(n))
```

















